---
title: "Writeup"
output: html_document
---

The goal of this work is to predict human activities by collected data using devices such as Jawbone Up, Nike FuelBand, and Fitbit. The approach of research is based upon this paper <http://groupware.les.inf.puc-rio.br/har>.

Environment initialization
===============================
Let us load these packages
```{r}
library(dplyr)
library(caret)
library(randomForest)
```

And set some seed to make the experiment reproducible

```{r}
set.seed(42)
```

Obtaining and preprocessing data
===============================

```{r}
if (!file.exists("pml-training.csv")){
  download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", destfile = "pml-training.csv", method="curl")  
}

# remove na and empty values from dataset
raw <- read.csv("pml-training.csv", na.strings = c("NA",""), stringsAsFactors = FALSE)

cleanupData = function(raw){
  # remove unrelated fields from model
  cleaned <- subset(raw, select = -c(X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window))
  cleaned
}

data = cleanupData(raw)
```

Prediction
=============================

Let us split train and test crossvalidation set in proportion of 70%/30%.
```{r}
data$classe <- as.factor(data$classe)  

testIndex = createDataPartition(data$classe, p = 0.7,list=FALSE)
train = data[-testIndex,]
test = data[testIndex,]

```

Based on the paper's rocommendations, we are going to use random forest classification algorithm.
```{r}
predictor <- randomForest(classe ~ ., data = train)
```

N.B.: for simplicity, single thread code has been provided. It can be run in parallel, using doParallel package (TBD: provide example).

Analysis
=============================

```{r}
testPred <- predict(predictor, newdata = test)
accurancy = confusionMatrix(crossValidation$classe, testPred)$overall[1]
```

So we can conclude that the algorithm's accurancy is equal to 98%.
